Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint

### 2014-11-13 intro.tex
started intro pass

Recently, an even higher level of geometric detail was reached in the
form of aligning
3D CAD models to real world test images~\cite{Aubry14,
  Lim14}. Interestingly, the problem of matching 3D models to 2D
images has been targeted since the early days of computer
vision~\cite{Lowe87}, but had largely been neglected in recent years
in favor of 2D detectors based on robust local features and
statistical learning techniques. Now, this problem is being revisited
mostly due to two reasons: the availability of sufficient artificial
3D training data and the availability of robust image matching
techniques.
%
% performance object detectors usually generalizes very well. It
% can handle various intraclass variability, viewpoint change and
% occlusion. However due to this high generalization, sometimes it is
% very difficult to get accurate pose, category or 2D-3D matching. Our
% method, specialized in giving such accurate information, can be
% applied on any generic object detectors to give high quality metadata.
% %
% Matching 3D CAD model to an image has been a classical problem that
% dates back to eighties . Lowe \etal , the vision
% community instead focused on the object detection tasks that estimates
% a rectangular bounding box around an object\cite{Felzenszwalb10,
%   Girshick14}. 
%
In addition, there has been a growing emand for accurate 2D-3D
matching \cite{Kholgade14, Chen13, Kostas14} for image manipulation,
editing, and data augmentation in the computer graphics community.
% Recently, with the powerful computing capabilities and a large
% collection of CAD models, the 2D-3D matching (registration) problem
% gets more and more approachable but due to inherent difficulty and
% limited performance of existing methods, many applications still
% require supervision to achieve 2D-3D matching.
% In medical community, registering 3D scan data to 2D image enabled various minimally invasive surgeries \cite{Markelj12}.

For category-level matching, \cite{Xiang12, Hejrati14, Pepik12} used
3D parts or aspect to represent underlying category-level 3D geometry
of the object. With the advent of large public CAD datasets
\cite{Trimble, Yobi}, the instance-level object detection and 2D-3D
registration became possible. \cite{Aubry14, Lim14} used large
collection of CAD models to faithfully align 3D CAD model to an image
by rendering CAD models and creating 2D templates for various
viewpoints.

Data-driven instance-level 2D-3D matching algorithms such as \cite{Aubry14, Lim14} require a large number of rendering and 2D templates for each of the CAD model with specific viewpoint. Since there are so many templates that it becomes almost impossible to get all the true positive image from training data. Instead \cite{Aubry14, Lim14} used whitening as a preprocessing stage \cite{Hariharan12} to make templates more discriminative. Then calibration is done on a small training dataset.

@@

\subsection{Approach Overview}

Our method is in line with \cite{Aubry14, Lim14} in the sense that we use only renderings not real images. However, rather than using fixed sized mid-level patches, we use whole object and make root templates. By using root templates, there is no need to learn a discriminative patch dictionary or to calibrate the patches and an additional inference stage is not required. However, whitening the whole template is prohibitive for several reasons. All templates have different aspect ratios making it difficult to generate the covariance matrix $\Sigma$. Since the root templates are larger than mid-level patches, a very large auto-covariance $\Gamma$ is required. Lastly, time complexity of decorrelating a template with $n$ cells increases as $O(n^3)$, resulting in slow template generation and large residuals due to numerical errors accumulated while decomposing the covariance matrix $\Sigma$.

>>>>

Recently, an even higher level of geometric detail was reached in the
form of aligning
3D CAD model instances to real world test images~\cite{Aubry14,
  Lim14,Kholgade14, Chen13, Kostas14}. Interestingly, the problem of matching 3D models to 2D
images has been targeted since the early days of computer
vision~\cite{Lowe87}, but had largely been neglected in recent years
in favor of 2D detectors based on robust local features and
statistical learning techniques. Now, this problem is being revisited
mostly due to two reasons: the availability of 3D CAD models for many
object classes and the availability of robust image matching
techniques.
%
% performance object detectors usually generalizes very well. It
% can handle various intraclass variability, viewpoint change and
% occlusion. However due to this high generalization, sometimes it is
% very difficult to get accurate pose, category or 2D-3D matching. Our
% method, specialized in giving such accurate information, can be
% applied on any generic object detectors to give high quality metadata.
% %
% Matching 3D CAD model to an image has been a classical problem that
% dates back to eighties . Lowe \etal , the vision
% community instead focused on the object detection tasks that estimates
% a rectangular bounding box around an object\cite{Felzenszwalb10,
%   Girshick14}. 
%
%In addition, there has been a growing emand for accurate 2D-3D
%matching \cite{Kholgade14, Chen13, Kostas14} for image manipulation,
%editing, and data augmentation in the computer graphics community.
%
% Recently, with the powerful computing capabilities and a large
% collection of CAD models, the 2D-3D matching (registration) problem
% gets more and more approachable but due to inherent difficulty and
% limited performance of existing methods, many applications still
% require supervision to achieve 2D-3D matching.
% In medical community, registering 3D scan data to 2D image enabled various minimally invasive surgeries \cite{Markelj12}.
%
% For category-level matching, \cite{Xiang12, Hejrati14, Pepik12} used
% 3D parts or aspect to represent underlying category-level 3D geometry
% of the object. With the advent of large public CAD datasets
% \cite{Trimble, Yobi}, the instance-level object detection and 2D-3D
% registration became possible. \cite{Aubry14, Lim14} used large
% collection of CAD models to faithfully align 3D CAD model to an image
% by rendering CAD models and creating 2D templates for various
% viewpoints.

Recent approaches to 2D-3D matching typically represent an object
class as a collection of 3D exemplar models, which they render from a
large number of viewpoints. The resulting artifial images are then
used to train exemplar models that can be matched to a real-world
image at test time.

\cite{Aubry14, Lim14} require a large number of rendering and 2D
templates for each of the CAD model with specific viewpoint. Since
there are so many templates that it becomes almost impossible to get
all the true positive image from training data. Instead \cite{Aubry14,
  Lim14} used whitening as a preprocessing stage \cite{Hariharan12} to
make templates more discriminative. Then calibration is done on a
small training dataset.

@@

\subsection{Approach Overview}
Our method is in line with \cite{Aubry14, Lim14} in the sense that we
use only renderings not real images. However, rather than using fixed
sized mid-level patches, we use whole object and make root
templates. By using root templates, there is no need to learn a
discriminative patch dictionary or to calibrate the patches and an
additional inference stage is not required. However, whitening the
whole template is prohibitive for several reasons. All templates have
different aspect ratios making it difficult to generate the covariance
matrix $\Sigma$. Since the root templates are larger than mid-level
patches, a very large auto-covariance $\Gamma$ is required. Lastly,
time complexity of decorrelating a template with $n$ cells increases
as $O(n^3)$, resulting in slow template generation and large residuals
due to numerical errors accumulated while decomposing the covariance
matrix $\Sigma$.
